\documentclass[a4paper, twoside, 12pt]{report}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
%top was 3cm

%% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[numbers, sort&compress]{natbib}

\usepackage{algorithm}
\usepackage[noEnd=false, indLines=false, spaceRequire=true, beginComment=//~]{algpseudocodex}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Assert:}}

\interfootnotelinepenalty=10000

% load some macros
\input{macros}

\title{Lightweight One-shot Imitation Learning}
\author{Alfie Chenery}
% Update supervisor and other title stuff in title/title.tex

\begin{document}
\input{title/title.tex}

\begin{abstract}
One-shot Imitation Learning is a leading approach in robotic learning, valued for minimizing the need for time consuming, human-collected demonstrations. However, the computational demands of these algorithms are substantial, limiting their usability in practical applications. What options exist when these requirements surpass available hardware capabilities? This paper explores alternatives to state of the art One-shot Imitation Learning algorithms and presents \socalled{LiteBot}, a system achieving comparable results with drastically reduced hardware requirements. This advancement lowers the barrier of entry, making such systems accessible to a wider audience, without the need for high-end GPUs.

%At a time where Moore's law appears to have begun to plateau, we can no longer simply rely on new hardware to be more powerful and speed up our algorithms.\\
%In the field of robotic learning, one-shot imitation learning stands as one of the best algorithms due to its ability to reduce the workload of engineers collecting demonstrations. Instead this workload is offloaded to the algorithm, which resultantly needs huge computational power to work. But what do we do when the algorithm requirements exceed that of our available hardware? In this paper we explore alternatives to current state of the art one-shot imitation learning algorithms, and create a system which can achieve comparable results, with drastically lower hardware requirements. This lowers the barrier to entry for such systems, allowing them to be run by more people, without top of the line GPUs. 
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
Firstly, I would like to thank my supervisor, Dr.~Edward Johns, for providing the opportunity to embark on this project. His guidance throughout this project have been invaluable in the face of countless implementation bugs. His expertise and detailed feedback have also helped to improve this project, and are greatly appreciated.
\\

I would like to personally thank my sayang, Nurdayana Muhd Faisal, for her help proof reading and her unending support through all the challenges of this year and those previous. I would likely not be at this point without her.
\\

I would like to thank my brother, for taking time out of his busy PhD to provide advice on writing this report. I would also like to thank my parents for always providing inspiration for me to strive for my best, and for agreeing to help proof read despite \speech{Not understanding a word of it.}
\\

Lastly, I would like to express my gratitude to all my friends for their continued support throughout my whole degree.
\end{abstract}

%title page, abstract and acknowledgements count towards report page limit, but latex only counts the title page, so manually inc by 2
\addtocounter{page}{2}

\tableofcontents
%\listoffigures
%\listoftables

\input{introduction.tex}
\input{background.tex}
\input{project.tex}
\input{evaluation.tex}
\input{future.tex}
\input{conclusion.tex}

\bibliographystyle{unsrtnat} %alpha
\bibliography{references}

\input{appendix.tex}

\end{document}